\documentclass[a4paper,11pt,twoside]{report}
\usepackage[utf8]{inputenc}
\usepackage[top=2.5cm,bottom=2.5cm,outer=2.5cm,inner=2.0cm]{geometry}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage{colortbl}
\usepackage{color,soul}
\usepackage{xcolor}

\usepackage{enumitem}
% \setlist[enumerate,1]{label=\color{blue}(\arabic*)}
\setlist[enumerate,1]{label=(\arabic*)}

\usepackage{graphicx}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{hyperref}
\hypersetup{
	colorlinks = true,
	linkbordercolor = {white},
}

\usepackage{listings}

\usepackage{setspace}
\renewcommand{\baselinestretch}{1.3}

\usepackage{siunitx}
\usepackage{threeparttable}
\usepackage{multirow}

\begin{document}
	
	\begin{center}
		{\large\textbf{MRM-25-26288.R1: Responses to Editors and Reviewers}}
	\end{center}
	
	% Robin: cortex / brain stem / hippocampus /
	
	% ========================================
	%     Editor
	% ========================================
	
	\noindent \underline{\textbf{Editor's Comments to the Author:}}
	
	\noindent \textit{Thanks for a well-received revision. The remaining minor point can be taken by editorial inspection without the need for further external review. We look forward to receiving your final revision. You may also wish to take this opportunity to ensure that your reference list is up to date and captures any recent relevant papers.}
	
	
	% ========================================
	%     Deputy Editor
	% ========================================
	\vspace{1em}
	
	\noindent \underline{\textbf{Deputy Editor: Wang, Shanshan Comments to Author:}}
	
	\noindent \textit{The revision is generally satisfying. There is still one minor concern. Please properly address it. Many thanks.}
	
	\vspace{1em}
	
	\hspace{1em} {\color{blue} We sincerely thank both editors and reviewers for the positive feedback. 
		We have addressed the remaining question.
	}
	
	% ========================================
	%     Reviewer 1
	% ========================================
	\vspace{3em}  % \clearpage
	\noindent \underline{\textbf{Reviewer 1}}
	
	\textit{The authors have addressed my comments and I recommend the manuscript for publication.}
		
	\hspace{1em} {\color{blue} Thank you for reviewing the manuscript.}

	% ========================================
	%     Reviewer 2
	% ========================================
	\vspace{3em}
	\noindent \underline{\textbf{Reviewer 2}}
	
	\textit{Thank you for addressing my previous concerns. I have one remaining question that I hope the authors can clarify:}
	
	\begin{enumerate}

		\item \textit{Did the authors apply any correction procedures to the acquired data? In the axial visualizations shown in Figures 5 and 6, the top of the head appears to exhibit some distortion.}
		
		\hspace{1em} {\color{blue} Thank you for the insight. 
			This work did not incorporate off-resonance correction in the reconstruction. 
			This has been discussed as one of the limitations in Discussion.
		}

	\end{enumerate}
	
\end{document}